A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-06-11 paper/paper.tex
updated graphs per TO DOs

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \caption{Global statistics. TO DO: CHANGE DIAMETER LABELS TO $1, H, 2, J, 3, 2H, 4, 2J$ AND PUT THESE ON HORIZONTAL AXIS. TO DO: CHANGE GRAPH TO SHOW SEPARATE DATA POINTS FOR EACH TOPOLOGICAL TYPE. TO DO: CREATE ANOTHER GRAPH WITH JUST EDGE DIAMETER COUNTS}
    \end{center}
    \caption{TO DO: ADD CAPTION}
    \label{fig:global_statistics}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \end{center}
    \caption{TO DO: ADD CAPTION}
    \label{fig:global_statistics_edges}
\end{figure}

>>>>

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/global_statistics.png}
    \end{center}
    \caption{Distribution of diameters.}
    \label{fig:global_statistics}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/split_statistics.png}
    \end{center}
    \caption{Distribution of diameters for each type.}
    \label{fig:type_statistics}
\end{figure}

\begin{figure}
    \begin{center}
    \includegraphics[width=0.6\linewidth]{figures/edge_diameters.png}
    \end{center}
    \caption{Distribution of diameters when only edges are considered, without hops or jumps.}
    \label{fig:global_statistics_edges}
\end{figure}
